On the uniqueness and stability of dictionaries for sparse representation of noisy signals

### 2017-08-17 manuscripts/PNAS/chazthm_pnas.tex
discussion

We prove Lem.~\ref{MainLemma} after stating auxiliary lemmas.% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.

>>>>

In this section, we prove Lem.~\ref{MainLemma} after stating auxiliary lemmas.% and then sketch the proofs of Thm.~\ref{robustPolythm} and Cor.~\ref{ProbabilisticCor}.
